### 2013-08-01 Tex/chapters/results.tex
Tabelle leicht verschönert
Ergänzung zum Grad K

        \begin{tabular}{l @{\quad} l l @{\quad} l l}

@@

@@

        K = \frac{\sum_{\avg{i,j}} 1}{\sum_{i} 1}

@@

@@

    graph. This is done in fig \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.

>>>>

        \begin{tabular}{l l l l l}

@@

            \cmidrule(rl){2-3} \cmidrule(rl){4-5}

@@

        K = \frac{1}{N} \sum_{\avg{i,j}} 1

@@

    The values for \(K\) are obtained as an average over \(100\)
    realizations of each graph type for \(L=16\) and \(L=32\) lattices.
    In fig. \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
    one can see, that these curves are almost identical and the small
    errorbars suggest, that they are sufficiently precise for this purpose.

@@

    graph. This is done in fig. \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.
